---
title: "Untitled"
author: "Katie Gao"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)
library(viridis)
```

TEST 123
testing 

```{r}
h1b_2018 = read.csv(file = "./data/dataset.csv")  
## this is a test to read and open the dataset
## I created a folder in our project called "data" 
## then inside it I downloaded the dataset and called it "dataset.csv" 



### this selects the 16 variables we are interested in
h1b_18_filter = h1b_2018 %>% 
  janitor::clean_names() %>% 
  select(case_number, visa_class, case_status, employer_name, employer_country, employer_city, employer_state,
         naics_code, soc_code, soc_name, total_workers, employment_start_date, employment_end_date, full_time_position,
         prevailing_wage, pw_unit_of_pay, worksite_city, worksite_state, h1b_dependent) %>%
  filter(case_status == "CERTIFIED",
          visa_class == "H-1B",
          employer_country == "UNITED STATES OF AMERICA") %>% 
  select(-visa_class, -case_status, -employer_country)

```

```{r}
library(ggplot2)
library(plotly)
```

```{r}
h1b_18_filter %>%
  group_by(employer_state) %>%
  summarize(state_n = n())
```


```{r}
<<<<<<< HEAD
 
```

=======
h1b_location =
  h1b_18_filter %>% 
  select(case_number, employer_city, employer_state, worksite_city, worksite_state) 

h1b_employer_50 = h1b_location %>% 
  filter(!employer_state %in% c("DC", "GU", "MP", "PR", "VI")) %>% 
  group_by(employer_state) %>% 
  summarize(employer_number = n()) %>% 
  rename("state" = "employer_state")

h1b_worksite_50 = h1b_location %>% 
  filter(!worksite_state %in% c("DC", "GU", "MH",  "MP", "PR", "VI")) %>% 
  group_by(worksite_state) %>% 
  summarize(worksite_number = n()) %>% 
  rename("state" = "worksite_state")


h1b_location_data_big = 
  full_join(h1b_employer_50, h1b_worksite_50, by = "state") %>% 
  filter(worksite_number >= 2000 | employer_number >= 2000) 
  
h1b_location_data_small =
  full_join(h1b_employer_50, h1b_worksite_50, by = "state") %>% 
  filter(worksite_number < 2000 & employer_number < 2000) %>% 
  mutate(employer_number = sum(employer_number),
         worksite_number = sum(worksite_number)) %>% 
  mutate(state = "Others") %>% 
  select(state, employer_number, worksite_number) 

others = unique(h1b_location_data_small) 

h1b_location_data = 
  bind_rows(h1b_location_data_big , others)
  

h1b_location_data %>% 
  mutate(state = fct_reorder(state, worksite_number)) %>% 
  plot_ly(x = ~state, y = ~employer_number, type = 'bar', name = 'headquater location') %>% 
  add_trace(y = ~worksite_number, name = 'work location') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'group', legend = list(x = 0.1, y = 0.9))
>>>>>>> 55da0ffbb28ced05a48a92b1a4967b20008fe176



## Map showing number of H1b in worksite state

```{r}
state_ws = 
  h1b_2018 %>%
  group_by(worksite_state) %>%
  summarize(n = n())
state_ws$hover <- with(state_ws, paste("State", worksite_state, "<br>", "Number", n))
g2 <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
map_2 <- plot_geo(state_ws, locationmode = 'USA-states') %>%
  add_trace(
    z = ~n, text = ~hover, locations = ~worksite_state,
    color = ~n, colors = 'Greens'
  ) %>%
  colorbar(title = "H1b Case Number") %>%
  layout(
    title = '2018 US H1b by worksite State',
    geo = g2
  )
map_2
```

<<<<<<< HEAD
=======



## Map showing number of H1b in worksite state

```{r}
state_ws = 
  h1b_2018 %>%
  group_by(worksite_state) %>%
  summarize(n = n())
state_ws$hover <- with(state_ws, paste("State", worksite_state, "<br>", "Number", n))
g2 <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
map_2 <- plot_geo(state_ws, locationmode = 'USA-states') %>%
  add_trace(
    z = ~n, text = ~hover, locations = ~worksite_state,
    color = ~n, colors = 'Greens'
  ) %>%
  colorbar(title = "H1b Case Number") %>%
  layout(
    title = '2018 US H1b by worksite State',
    geo = g2
  )
map_2
```

>>>>>>> 55da0ffbb28ced05a48a92b1a4967b20008fe176
## Map showing number of H1b in employer state

```{r}
state_number = 
  h1b_2018 %>%
  group_by(employer_state) %>%
  summarize(n = n())

state_number$hover <- with(state_number, paste("State", employer_state, "<br>", "Number", n))

l <- list(color = toRGB("white"), width = 2)

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

p <- plot_geo(state_number, locationmode = 'USA-states') %>%
  add_trace(
    z = ~n, text = ~hover, locations = ~employer_state,
    color = ~n, colors = 'Purples'
  ) %>%
  colorbar(title = "Millions USD") %>%
  layout(
    title = '2018 US H1b by State',
    geo = g
  )

p
```

<<<<<<< HEAD
##Graph showing top 10 cities with H1b cases in California state (worksite)
=======
## Graph showing top 10 cities with H1b cases in California state (worksite)
>>>>>>> 55da0ffbb28ced05a48a92b1a4967b20008fe176

```{r}
city_ca = 
  h1b_2018 %>%
  filter(worksite_state == 'CA') %>% 
  group_by(worksite_city) %>%
  summarize(n = n()) %>% 
  filter(min_rank(desc(n)) <= 10)
city_ca %>% 
  mutate(worksite_city = fct_reorder(worksite_city, n)) %>% 
  plot_ly(x = ~worksite_city, y = ~n, color = ~worksite_city, type = "bar")
<<<<<<< HEAD
```
=======
```


## Companies that have the most H1B Visa Workers
```{r}
h1b_soc = h1b_18_filter %>% 
    select(case_number, employer_name, naics_code, soc_code, soc_name, total_workers, employment_start_date, employment_end_date, full_time_position)

  
h1b_soc_con = h1b_soc %>% 
  select(employer_name, total_workers) %>% 
  group_by(employer_name) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  top_n(15)

h1b_soc_con
  
h1b_soc_con %>% 
  ggplot(aes(x = reorder(employer_name, total), y = total)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(x = 'Companies', y = 'Total Workers', 
       title = 'Top 15 companies who has the most H1B Visa Workers')

```
  
  
  
  
Regrouping SOC codes broadly - use bls website as source
```{r}
h1b_soc_ind = h1b_soc %>%
  select(soc_code) %>% 
  mutate(soc_code_new = str_remove_all(soc_code, '-'),
         soc_code_new = as.integer(soc_code_new)) %>% 
  na.omit() %>% 
  mutate(soc_code_gen = case_when(
    soc_code_new >= 110000 & soc_code_new < 120000 ~ "Management",
    soc_code_new >= 130000 & soc_code_new < 140000 ~"Business, Finance",
    soc_code_new >= 150000 & soc_code_new < 160000 ~ "Computer, Math",
    soc_code_new >= 170000 & soc_code_new < 180000 ~ "Architecture, Engineer",
    soc_code_new >= 190000 & soc_code_new < 200000 ~ "Life, Physcial, Social Science",
    soc_code_new >= 210000 & soc_code_new < 220000 ~ "Social Service",
    soc_code_new >= 230000 & soc_code_new < 240000 ~ "Legal",
    soc_code_new >= 250000 & soc_code_new < 260000 ~ "Education, Training",
    soc_code_new >= 270000 & soc_code_new < 280000 ~ "Media, Design",
    soc_code_new >= 290000 & soc_code_new < 300000 ~ "Healthcare Practitioner",
    soc_code_new >= 410000 & soc_code_new < 420000 ~ "Sales",
    TRUE ~ "Others")) %>% 
  mutate(soc_code_gen = as.factor(soc_code_gen))
  
h1b_soc_ind
```
  
  
## Certified H1B applicants and which industries they are in
```{r}
h1b_soc_small = h1b_soc_ind %>%
  group_by(soc_code_gen) %>%
  summarize(num_ind = n()) %>% 
  arrange(desc(num_ind)) %>% 
  mutate(soc_code_gen = fct_reorder(soc_code_gen, num_ind))
  
#h1b_soc_plot = h1b_soc_small %>% 
  #ggplot(aes(x = reorder(soc_code_gen, num_ind), y = num_ind)) +
  #geom_bar(stat = 'identity') +
  #coord_flip() +
  #labs(x = 'Industries', y = 'Total Workers', 
       #title = 'Industries and number of certified H1B appliants')

h1b_soc_plot = plot_ly(
    h1b_soc_small, x = ~soc_code_gen, y = ~num_ind, color = ~soc_code_gen, type = "bar", colors = "Set1"
    ) %>% 
        layout(title = 'Industries and number of certified H1B applicants',
           xaxis = list(title = 'Industries'),
           yaxis = list(title = 'Total Workers'), 
           showlegend = FALSE)

h1b_soc_plot
```
 
 
## Length of time employees were contracted.
```{r}
library(lubridate)
h1b_soc_date <- h1b_soc %>%
  select(employment_start_date, employment_end_date) %>%
  mutate(employment_start_date = as.Date(employment_start_date),
         employment_end_date = as.Date(employment_end_date),
         year_start = year(employment_start_date),
         year_end = year(employment_end_date),
         length_time = year_end - year_start, 
         length_time= as.factor(length_time))
date_table <- h1b_soc_date %>%
  group_by(length_time) %>%
  summarize(num_year = n())


ggplot(data = h1b_soc_date, aes(x = length_time)) +
  geom_bar()


str(h1b_soc_date)
h1b_soc_date
```


```{r}
money = h1b_18_filter %>% 
  select(prevailing_wage, pw_unit_of_pay) 
summary(money)
```


## Converting wage to the same units 
```{r}
## this creates a new column for the adjusted wage per year 
h1b_18_adjusted_wage = 
  h1b_18_filter %>% 
  mutate(pw_unit_of_pay = str_to_lower(pw_unit_of_pay), 
         adjusted_wage_per_year = prevailing_wage)  

## we know that there are 5 levels for pw_unit_of_pay
## year, hour, week, month, bi-weekly 

## this converts all pay wages to yearly 
h1b_18_adjusted_wage = 
  h1b_18_adjusted_wage %>%
##select(pw_unit_of_pay, adjusted_wage_per_year, prevailing_wage) %>% 
  mutate(adjusted_wage_per_year = 
           if_else(pw_unit_of_pay == "hour", prevailing_wage * 40 * 52, 
                   if_else(pw_unit_of_pay == "week", prevailing_wage * 52, 
                           if_else(pw_unit_of_pay == "month", prevailing_wage * 12, 
                                   if_else(pw_unit_of_pay == "bi-weekly", prevailing_wage * 26, 
                                           prevailing_wage)))))

```




